The primary objective of this work was to support to continuing research with
JSPAM by building a standardized framework through which future projects can
interact with the JSPAM code.
We have accomplished this objective by establishing a working framework
that retrieves the appropriate data, executes the JSPAM code efficiently, stores
and organizes the output of JSPAM, and encapsulates all relevant data and
meta-data in instances of a \texttt{MergerRun} object.
Further, although not discussed in this paper as it was not the focus of this
work, the storage scheme does make further analysis and image creation
substantially easier, and \texttt{jspamcli.py} was successfully used
with a elementary approach at comparison of simulation images and real SDSS DR7, DR8,
and DR9 images prepared with MergerEx.

There now exists a dedicated
\texttt{MergerRun} class with member functions that implement most necessary tasks
relating to the merger data. Rather than deal with data input and output
on a case by case
basis, we can now instantiate this class to encapsulate all necessary data for
operations common to analysis of mergers in the context with which we are
concerned. Further, the output from all member functions has been logically
structured to reduce future headaches that come from handling large volumes
of file input and output.
There also exist several member functions only briefly mentioned here that aid in visualization
of the mergers from start to finish.

The \texttt{MergerRun} class is used extensively in what we dub the JSPAM Command
Line Interface (\texttt{jspamcli.py}). This program makes interacting with
the JSPAM code a bit more straightforward and gives the user several modes of
interaction that we found to be useful in different contexts. Further, we have
now standardized input and output from JSPAM so that future work on the project can rely on
predictable behavior.

We also created an option to execute \texttt{basic\_run} asynchronously across
a variable number of cores. While we have not strictly parallelized
\texttt{basic\_run}, we've distributed its execution to make more efficient use
of powerful workstations that are readily available.
